---
title: "TINC analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TINC analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE, message=FALSE}
library(TINC)
```
# Analysis pipeline

The TINC pipelines requires to run a single function: `autofit`.

Results can then be inspected using two report functions (see below).

# Example simulated inputs

TIN provides a function to generate a random dataset to test the tool. The input `TIN` and `TIT` parameters
can be specified.

> Note: the sampler generates VAFs using [MOBSTER](https://caravagnalab.github.io/mobster/), and then samples some  clonal mutations and contaminates the normal. This process is noisy and might return slightly lower values for the actual `TIT` estimate. The best setup to test TINC is with a simulated BAM file - e.g., created via [BAMSurgeon](https://github.com/adamewing/bamsurgeon).

```{r, message=FALSE, warning=F, fig.width=6, fig.height=4}
set.seed(1234)

# Sample data from a tumour with 80% purity, and 10% contamination in the normal
sampled_data = random_TIN(TIT = .8, TIN = 0.1)

print(sampled_data)
```

The sampler generates random SNVs, and plain diploid CNA segments. These segments are not real and span just
through each one of the simulated SNVs.

Data mappings - done internally by TINC - are also available via the `load_TINC_input` function.

```{r}
load_TINC_input(x = sampled_data$data, cna = sampled_data$cna)
```

TINC fits the data via the `autofit` function.

A flag `FAST` sets faster set of parameters to determine TIN and TIT scores - we usually this for prototyping analyses and then turn it to `FALSE`.

```{r, message=TRUE, warning=F}
# Autofit function
TINC_fit = autofit(sampled_data$data, cna = NULL, FAST = TRUE)
```

Summary of the results (with an S3 object)
```{r, message=TRUE, warning=F}
print(TINC_fit)
```

Plot the results (with an S3 object).
```{r, message=FALSE, warning=F, fig.width=10, fig.height=4}
plot(TINC_fit)

# Analogous to
# plot_simple_report(TINC_fit)
```

Or make a more detailed report
```{r, message=FALSE, warning=F, fig.width=10, fig.height=10}
plot_full_page_report(TINC_fit)

```

A similar fit object is available inside the package (called `fit_example`).
